---
title: EEE933 - Design and Analysis of Experiments

# Use letters for affiliations
author:
  - name: Case Study 01

# For footer text  TODO(fold into template, allow free form two-authors)
#lead_author_surname: ELE077 - TC1

# Place DOI URL or CRAN Package URL here
#doi: "https://cran.r-project.org/package=YourPackage"

# Abstract
abstract: |
  Experiment: performance of a new software version.

# Optional: Acknowledgements
# acknowledgements: |
#   This template package builds upon, and extends, the work of the excellent 
#   [rticles](https://cran.r-project.org/package=rticles) package, and both rely on
#   the [PNAS LaTeX](http://www.pnas.org/site/authors/latex.xhtml) macros. Both sources
#   are gratefully acknowledged as this work would not have been possible without them.
#   Our extensions are under the same respective licensing term 
#   ([GPL-3](https://www.gnu.org/licenses/gpl-3.0.en.html) and
#   [LPPL (>= 1.3)](https://www.latex-project.org/lppl/)).

# Optional: One or more keywords
# keywords:
#   - one
#   - two
#   - optional
#   - keywords
#   - here

# Font size of the document, values of 9pt (default), 10pt, 11pt and 12pt
fontsize: 11pt

# Optional: Force one-column layout, default is two-column
one_column: true

# Optional: Enables lineo mode, but only if one_column mode is also true
#lineno: true

# Optional: Enable one-sided layout, default is two-sided
#one_sided: true

# Optional: Enable section numbering, default is unnumbered
#numbersections: true

# Optional: Specify the depth of section number, default is 5
#secnumdepth: 5

# Optional: Bibliography 
#bibliography: pinp

# Optional: Enable a 'Draft' watermark on the document
#watermark: true

# Customize footer, eg by referencing the vignette
#footer_contents: "YourPackage Vignette"

# Optional: Skip inserting final break between acknowledgements, default is false
skip_final_break: true

# Produce a pinp document
output: pinp::pinp


# Required: Vignette metadata for inclusion in a package.
#vignette: >
#  %\VignetteIndexEntry{YourPackage-vignetteentry}
#  %\VignetteKeywords{YourPackage, r, anotherkeyword}
#  %\VignettePackage{YourPackage}
#  %\VignetteEngine{knitr::rmarkdown}
---


# The experiment  

The **current** version of a given system is known, based on extensive past experience, to have a distribution of execution costs with populational mean $\mu = 50$ and populational variance $\sigma^2 = 100$ (the specific units are not important in this particular experiment). Notice that these are considered populational parameters, not sample estimates.

A **new** version of this software is developed, and we wish to investigate whether it results in _performance improvements_ (e.g., smaller mean execution cost and/or smaller variance) in relation to the current standard. To investigate this particular question, an experimental analysis will be performed.

To **simulate** the data collection procedures for the **new** software version, the following routines will be used. First, to set up the data collection procedure, use:

``` {r, eval = FALSE}
# Install required package and set up simulation
install.packages("ExpDE") # <-- you only need to install it once
```
``` {r}
# Set up the data-generating procedure
library(ExpDE)
mre <- list(name = "recombination_bin", cr = 0.9) 
mmu <- list(name = "mutation_rand", f = 2)
mpo <- 100
mse <- list(name  = "selection_standard")
mst <- list(names = "stop_maxeval", maxevals = 10000)
mpr <- list(name  = "sphere", xmin  = -seq(1, 20), xmax  = 20 + 5 * seq(5, 24))
```

A **single** observation of running cost for the **new** version can be obtained by running:

```{r}
# Generate a single observation
ExpDE(mpo, mmu, mre, mse, mst, mpr,
      showpars = list(show.iters = "none"))$Fbest
```

***
\newpage
# Activities  

## For the test on the mean cost  

For this test, assume a desired significance level $\alpha = 0.01$, a minimally 
relevant effect size of $\delta^* = 4$, and a desired power of $\pi = 1 - \beta = 0.8$. 
Each team must perform the following activities:

- Define the statistical hypotheses to be tested (null/alternative).
- Define the sample size to be used in this experiment, and collect the sample.
- Test the hypotheses and decide for rejecting (or not) the null hypothesis.
- Calculate the confidence interval on the mean.
- Validate and discuss the assumptions of the test.
- Discuss the power of the test (if needed), and the adequacy of the sample size used for this particular test.


## For the test on the variance of the cost  

For this test, assume a desired significance level $\alpha = 0.05$. Assume also 
that reductions in standard deviation is a secondary benefit, to be investigated 
using the same observations collected for the first test. Each team must perform 
the following activities:

- Define the statistical hypotheses to be tested (null/alternative).
- Test the hypotheses and decide for rejecting (or not) the null hypothesis.
- Calculate the confidence interval on the variance.
- Validate and discuss the assumptions of the test.


After performing the activities related to each test individually, the team must:

- Draw conclusions and provide recommendations regarding the adoption (or not) of the new software version.
- Discuss possible ways to improve this experiment.


## [Bonus question]  

Can you also provide a 90\% tolerance interval (using a confidence level $\alpha = 0.05$) for the population of running costs? Notice that the data may not be Normal.

***
\newpage
# Report  

Each team must prepare a short report detailing the experiment and the analysis performed. The report will be evaluated according to the following criteria:

- Use of the predefined format (see below);
- Reproducibility of the analyses;
- Technical quality;
- Logical structure;
- Correct use of language (grammar, orthography, _etc._);

The report must **necessarily** be prepared using [R Markdown](http://rmarkdown.rstudio.com), and must contain the full code needed to reproduce the analysis performed by the team, embedded in the form of _code blocks_. Each team must deliver the following files:

- The report file, compiled in **.pdf** .
- The original (**.Rmd** source file) of the report.
- The data file (**.csv**) generated in this experiment.

The **.Rmd** file must be able to be recompiled, if needed (tip: save your **.Rmd** file using UTF-8 encoding, to prevent compilation problems in other operational systems. 

Report templates are available on  [https://git.io/vHk0F](https://git.io/vHk0F), and an example of report structure can be consulted on [https://git.io/vHk0j](https://git.io/vHk0j). This document can also be used as a template.

**Important**: Please include in the report the roles of each team member (Coordinator, Recorder, Checker and, for 4-member teams, Monitor)

**Important**: Reports can be prepared in either Portuguese or English.

***

# Deadline  

The report files (pdf + rmd + csv) must be compressed into a single file (use **.ZIP**) and uploaded to the activity **Case Study 01** on Moodle, until **Monday, September 24 2018, 11:59p.m.**. After that deadline the system will be closed. 

**Important**: Only ONE submission is required for each team.

**Important**: Reports will NOT be received by e-mail or in printed form.